---
title: "Intro to Data Visualization with ggplot"
subtitle: "Strauss Health Sciences Library"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  revealjs::revealjs_presentation:
    transition: none
---
<!-- Have to put these styles 'cause pandoc+revealjs not working -->
<style>
.column-left{
  float: left;
  width: 60%;
  text-align: left;
}
.column-right{
  float: right;
  width: 40%;
  text-align: right;
}
</style>
```{r setup, include=FALSE}
library(tidyverse)
```

# What is the Grammar of Graphics?


# How is the Grammar of Graphics Implemented in ggplot?


# How do these layers apply to your graph?

> -  aes -> how the data variables map to the elements in the graph (axes, point size, ...)
> -  geom -> how the data is represented (type of plotting: scatter, line, ...)

# Schematic of ggplot syntax
```{r example, eval=FALSE}
p <- ggplot(data=<data>,
            mapping=aes(<aesthetic> = variable,
                        <aesthetic> = variable,
                        <...> = ...)

p + geom_<type>(<...>)+
scale_<mapping>_<type>(<...>)+
coord_<type>(<...>)+
labs(<...>)
```

# Could it be this difficult?
::: {.column-left}
```{r echo=TRUE,eval=FALSE}
plot(iris[,-5])
```
:::
::: {.column-right}
```{r echo=FALSE}
plot(iris[,-5])
```
:::

# Help me out with this survey

https://bit.ly/StraussClass


  